The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-14 paper/iphas-dr2.tex

\begin{abstract} % BACKGROUND, OBJECTIVE, METHODS, RESULTS, CONCLUSIONS
The INT/WFC Photometric H$\alpha$ Survey 
of the Northern Galactic Plane (IPHAS)
is a 1800 deg$^2$ imaging survey
covering the entire northern Milky Way at $|b| < 5^\circ$
in the $r$, $i$ and \ha\ filters 
using the Wide Field Camera (WFC) 
on the 2.5-meter Isaac Newton Telescope (INT) in La Palma.
We present the first quality-controlled and
uniformly-calibrated source catalogue
to have been extracted from the images,
providing single-epoch photometry
for 219 million unique sources
across 92\% of the survey area.
The observations were carried out between 2003 and 2013
at a median seeing of 1.1 arcsec
and to a depth of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$ and \ha$=20.3\pm 0.3$
($5\sigma$ limits, Vega system).
We explain the data reduction 
and quality control procedures,
describe and test the new uniform calibration,
and detail the construction of the 97-column source catalogue.
We show that the calibration
and the photometric repeatability are accurate to
0.03~mag (rms),
and provide a series of recommended quality criteria
which can be used to select the most reliable data
from the catalogue.
Finally, we demonstrate the ability of the 
catalogue's unique
$(r-i)$/($r-\ha)$ colour-colour diagram to
(i) characterise stellar populations and extinction regimes
towards different Galactic sight-lines
and (ii) select candidate \ha\ emission-line objects.
IPHAS is the first survey to offer comprehensive CCD photometry
of point sources across the Galactic Plane at visible wavelengths,
providing the much-needed counterpart
to infrared surveys,
whilst also providing images for some of the most
crowded regions to be faced by Gaia.
\end{abstract}

>>>>

\begin{abstract} % BACKGROUND, OBJECTIVE, METHODS, RESULTS, CONCLUSIONS
The INT/WFC Photometric H$\alpha$ Survey 
of the Northern Galactic Plane (IPHAS)
is a 1800 deg$^2$ imaging survey
covering the entire northern Milky Way at $|b| < 5^\circ$
in the $r$, $i$ and \ha\ filters 
using the Wide Field Camera (WFC) 
on the 2.5-meter Isaac Newton Telescope (INT) in La Palma.
We present the first quality-controlled and
uniformly-calibrated source catalogue
to have been extracted from the images,
providing single-epoch photometry
for 219 million unique sources
across 92\% of the survey area.
The observations were carried out between 2003 and 2013
at a median seeing of 1.1 arcsec
and to a mean depth of $r=21.2$ / $i=20.0$ / $\ha=20.3$
($5\sigma$ limits, Vega system).
We explain the data reduction 
and quality control procedures,
describe and test the new uniform calibration,
and detail the construction of the 97-column source catalogue.
We show that the global calibration is accurate to
0.03~mag (rms) by validating against SDSS,
and provide a series of recommended quality criteria
which can be used to select the most reliable data
from the catalogue.
Finally, we demonstrate the ability of the 
catalogue's unique
$(r-i)$/($r-\ha)$ colour-colour diagram to
(i) characterise stellar populations and extinction regimes
towards different Galactic sight-lines
and (ii) select candidate \ha\ emission-line objects.
IPHAS is the first survey to offer comprehensive CCD photometry
of point sources across the Galactic Plane at visible wavelengths,
providing the much-needed counterpart
to infrared surveys.
We also provide images for some of the most
crowded regions to be faced by Gaia.
\end{abstract}
